Data Exploration

### 2019-01-10 src/data_exploration.Rmd
figuring out if gear is a factor...

@@

@@

dunn test (not working)
```{r}
gear_temp_depthdunn <- dunnTest(presence$temp_depth, presence$gear)

write.csv(gear_temp_depthdunn, "../output/env/gear_temp_depthdunn.csv", row.names = TRUE)
```

>>>>

add nafo region and gear type into the mix

first subset the env.correlate columns + bottom_depth (you don't need everything)

```{r}
background_envbotdepth <- subset(background, select = c(amo_sample, amo_winter, amo_prev, nao_sample, nao_winter, nao_prev, chl_surface, chl_depth, mlp_surface, ssh_surface, temp_surface, temp_depth, o2_surface, o2_depth, salinity_surface, salinity_depth, bottom_depth))
background_envbotdepth_cor <- cor(background_envbotdepth, use="complete.obs", method = "spearman") #need to create a correlation using cor to plot. complete.obs means na.rm in this package. #using spearmans as suitable for non-linear relationships
write.csv(background_envbotdepth_cor, "../output/env/background_envbotdepth_cor.csv", row.names = TRUE)
background_corrplot <- corrplot(background_envbotdepth_cor , method = "color", type = "upper", order = "alphabet", tl.cex = 0.8) 
dev.copy(png,"../output/env/simple_plots/background_envbotdepth_cor.png") # to automatically save the plot to a png AND show it inline
dev.off() # stops automatic saving of the plot to a png
```

@@

map the gear usage in Arcgis (gear_type_map)

create a table of gear use by month

```{r}
gearby_mth <- with(presence, table(month, gear))
write.csv(gearby_mth, file = "../output/bio/gear_by_mth.csv")
gearby_mth
```

@@

dunn test 
```{r}
gear_temp_depthdunn <- dunnTest(presence$temp_depth, presence$gear, list = TRUE)
gear_temp_depthdunn

write.csv(table, "../output/env/gear_temp_depthdunn.csv", row.names = TRUE)
```
